Attack Graph Generation for Microservice Architecture

### 2018-10-21 paper_own_docker/chapters/conclusion.tex
Related work and conclusion updated based on proof-reading feedback

Microservices are a promising architectural style that advocate practitioners to build systems as a group of small connected  services. Although this style enables better scalability and faster deployment, the full container-based automation within this style raises many security concerns. In this paper, we proposed to use automated attack graph generation as part of the practices of developing microservice-based architectures. Attack graphs aid the developers in identifying attack paths that consist of multiple vulnerability exploitation in the deployed services. The manual construction of attack graphs is an error-prone, resource consuming activity. Hence, automating this process does not only guarantee efficient construction but also complies with the spirit of DevOps practices. We have shown that such automation, extending previous works in computer networks field, is efficient and scales to complex and big microservice-based systems.

As a future work, we plan to extend this work to support more frameworks that are used in microservices systems. We also plan to study the possible analysis of the resulting attack graphs for purposes of attack detection, and post-postmortem forensics investigations.

>>>>

Microservices are a promising architectural style that encourage practitioners to build systems as a group of small connected  services. Although such architectures can realize better scalability and faster deployment, full container-based automation raises many security concerns. In this paper, we have proposed the use of automated attack graph generation relative to the development of microservice-based architectures. Attack graphs help developers identify attack paths that comprise exploitable vulnerabilities in deployed services. Manual construction of attack graphs is an error-prone, resource consuming activity; therefore, automating this process guarantees efficient construction and complies with the spirit of DevOps practices. By extending previous work in field of computer networks, we have demonstrated that such automation is efficient and scales to large and complex microservice-based systems.

In future work, we plan to extend this work to support more frameworks used in microservice systems. We also plan to study possible analysis of the resulting attack graphs for use in attack detection and post-postmortem forensics investigations.

### 2018-10-21 paper_own_docker/chapters/related_work.tex
last round of fixes
Related work and conclusion updated based on proof-reading feedback

Previous work has dealt with attack graph generation, mainly in computer networks \cite{ingols2006practical, sheyner2002automated, ritchey2000using, ou2006scalable}, where multiple machines are connected to each other and the Internet. %In these networks, an attacker performs multiple steps to achieve his goal, i.e., gaining privileges of a specific host. Attack graphs help in analyzing this behavior. Although attack graphs are useful, constructing them manually can be a cumbersome and time-consuming process. Tools that generate vulnerabilities of a specific host are available \cite{clair, artz2002netspa, farmer1990cops}. However previous works state that these tools alone are not enough to analyze the vulnerability of an entire network and that these tools in addition to network topology could solve this issue. This outcome is because different hosts are connected together and influence the outcome of an attack. Therefore, some teams have been working on developing systems that generate attack graphs automatically by using different approaches.
One of the earlier works in attack graph generation was done by Sheyner et al. by using model checkers with goal property \cite{sheyner2002automated}. Model checkers use computational logic to check if a model is correct, and otherwise, they provide a counterexample. A collection of these counterexamples form an attack graph. They state that model checkers satisfy a monotonicity property  to ensure termination. However, model checkers have a computational disadvantage. %In the example provided, NuSMV takes 2 hours to construct the attack graph with 5948 nodes and 68364 edges . As a result of this, more scalable approach was needed.
 Amman et al. extend this work with some simplifications and more efficient storage \cite{ritchey2000using}. Ou et al. use a logical attack graph \cite{ou2006scalable} and Ingols \cite{ingols2006practical} et al. use a Breadth-first search algorithm in order to tackle the scalability issue. Ingols et al. discuss the redundancy Full and Predictive graphs and model an attack graph as an MP graph with content-less edges and 3 types of nodes. They use Breath-first search technique for generating the attack graph. This approach provides faster results in comparison to using model checkers. An MP graph of 8901 nodes and 23315 edges is constructed in 0.5 seconds. Aksu et al. build on top of Ingols's system and evaluate a set of rule pre- and postconditions in generating attacks. They define a specific test of pre- and postcondition rules and test their correctness. In their evaluation, they use a machine learning approach \cite{aksu2018automated}.

Containers and microservice architectures, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their  need of connectivity and a lesser degree of encapsulation \cite{combe2016docker, dragoni2017microservices}. To the best of our knowledge, no previous work that has been done  in the area of attack graph generation for Docker containers. Similar to computer networks, microservice architectures have a container topology and tools for analysis of containers. Containers in our model correspond to hosts, and a connection between hosts translates to communication between containers.

In summary, our contribution is proposing attack graph generation as part of the DevOps practices, and providing a tool-support for this idea. To that end, we extended the work from Ingols \cite{ingols2006practical} and Aksu \cite{aksu2018automated} in conjunction with Clair OS to generate attack graphs for microservice architectures.

>>>>

Previous studies have examined attack graph generation, primarily relative to computer networks \cite{ingols2006practical, sheyner2002automated, ritchey2000using, ou2006scalable}, where multiple machines are connected to each other and the Internet. %In these networks, an attacker performs multiple steps to achieve his goal, i.e., gaining privileges of a specific host. Attack graphs help in analyzing this behavior. Although attack graphs are useful, constructing them manually can be a cumbersome and time-consuming process. Tools that generate vulnerabilities of a specific host are available \cite{clair, artz2002netspa, farmer1990cops}. However previous works state that these tools alone are not enough to analyze the vulnerability of an entire network and that these tools in addition to network topology could solve this issue. This outcome is because different hosts are connected together and influence the outcome of an attack. Therefore, some teams have been working on developing systems that generate attack graphs automatically by using different approaches.
One early study of attack graph generation was conducted by Sheyner et al. using model checkers with a goal property \cite{sheyner2002automated}. Model checkers use computational logic to determine if a model is correct; otherwise, if the model is incorrect, the model checkers provide a counterexample. A collection of these counterexamples form an attack graph. Sheyner et al. stated that model checkers satisfy the monotonicity property to ensure termination. However, model checkers have a computational disadvantage. %In the example provided, NuSMV takes 2 hours to construct the attack graph with 5948 nodes and 68364 edges . As a result of this, more scalable approach was needed.
 Amman et al. extended this work with some simplifications and more efficient storage \cite{ritchey2000using}. Ou et al. used a logical attack graph \cite{ou2006scalable} and Ingols et al. \cite{ingols2006practical} used BFS algorithm to tackle the scalability issue. Ingols et al. discussed the redundancy of full and predictive graphs and modeled an attack graph as an MP graph with contentless edges and three node types. They used BFS technique to generate the attack graph. This approach provides faster results compared to using model checkers. For example, with this method, an MP graph with 8901 nodes and 23315 edges was constructed in 0.5 seconds. Aksu et al. conveyed a study on top of Ingols's system. They defined a specific set of precondition and postcondition rules and tested their correctness. Note that they used a machine learning approach in their evaluation \cite{aksu2018automated}.

Despite their increasing popularity, containers and microservice architectures have demonstrated serious security risks, primarily due to their connectivity requirements and lesser degree of encapsulation \cite{combe2016docker, dragoni2017microservices}. To the best of our knowledge, no previous study has been conducted relative to attack graph generation for Docker containers. Similar to computer networks, microservice architectures have a container topology and tools for container analysis. Containers in our model correspond to hosts, and a connection between hosts translates to communication between containers.

In summary, our contribution is using attack graph generation as part of DevOps practices and providing tool support for this concept. To that end, we have extended the work of Ingols \cite{ingols2006practical} and Aksu \cite{aksu2018automated} in conjunction with the Clair OS to generate attack graphs for microservice architectures.
